The Warrior Stabs the Goat: Creating a Dothraki Resource Grammar with Grammatical Framework

### 2016-10-16 documentation/paper.tex
Typos

Of course, it is not feasible either to implement the entire
resource grammar before being able to do any kind of testing.
As a remedy for this problem, Ranta recommends
taking the resource grammar of a similar language as a
starting point and changing it step 
by step \cite[p.\ 224]{gf-book}. 
This proved difficult in our case, since Dothraki, as a constructed
language, of course does not have family ties to any existing language. 
While its grammar is certainly inspired by phenomena seen in
natural languages, these appear to be picked from a variety
of different language families (many of which, as non-linguists, we are not
particularly familiar with). Furthermore, taking
a language like English as a starting point, which is certainly similar
to Dothraki in many aspects, but wildly different in others,
proved to be fraught with difficulties as well. This is because
of the web of dependencies in a grammar,
changes at one point, such as increasing the number of cases 
from two to five, tend to require changes in a number
of different places all over the grammar, an effect that
can quickly snowball. Finding our own solution for
this problem, namely growing the abstract part gradually 
(by selectively copying over parts from the full RGL) along with
the concrete implementation, took time, but in the end we 
are satisfied with how it turned out.

@@

>>>>

Of course, implementing the entire
resource grammar before being able to do any kind of testing
is not a feasible strategy either.
As a remedy for this problem, Ranta recommends
taking the resource grammar of a similar language as a
starting point and changing it step 
by step \cite[p.\ 224]{gf-book}. 
This proved difficult in our case, since Dothraki, as a constructed
language, of course does not have family ties to any existing language. 
While its grammar is certainly inspired by phenomena seen in
natural languages, these appear to be picked from a variety
of different language families (many of which, as non-linguists, we are not
particularly familiar with). Furthermore, taking
a language like English as a starting point, which is certainly similar
to Dothraki in many aspects, but wildly different in others,
proved to be fraught with difficulties as well. This is because
of the web of dependencies in a grammar,
changes at one point, such as increasing the number of cases 
from two to five, tend to require changes in a number
of different places all over the grammar, an effect that
can quickly snowball. Finding our own solution for
this problem, namely growing the abstract part gradually 
(by selectively copying over parts from the full RGL) along with
the concrete implementation, took time, but in the end we 
are satisfied with how it turned out.

@@

\newpage
\thispagestyle{empty}

{\LARGE Versicherung}

\vspace{1cm}
Hiermit versichern wir, diese Arbeit selbst\"andig verfasst und keine anderen als
die angegebenen Quellen benutzt zu haben. Wir versichern ferner, dass diese
Arbeit oder Teile davon nicht schon für eine andere Abschlusspr\"ufung oder einen 
anderen Beteiligungsnachweis eingereicht wurden. Uns ist bewusst, dass ein 
Zuwiderhandeln gegen diese Versicherung eine Ordnungswidrigkeit darstellt, die 
mit einer Geldbu\ss e geahndet werden kann.

\vspace{1cm}
D\"usseldorf, den 16.10.2016
